---
title: "trash"
format: html
editor: visual
---



## Git is totally integrated with R {background-image="./images/sisyphus.jpeg" background-opacity="0.2"}

### (some effort needed)

<br>

::: panel-tabset
### First Step

#### Windows

-   Download [R](https://cran.r-project.org/bin/windows/base/) and [RStudio](https://posit.co/products/open-source/rstudio/)

-   Register a [GitHub](https://github.com/) account

-   Install [Git](https://git-scm.com/downloads)

-   [GitHub Desktop](https://desktop.github.com/) - Optional

#### Mac

```{r eval=FALSE}
#| class-output: big-code
#| 
$ git --version

$ git config

```

### Second Step

<br>

#### Personal Access Token (PAT):

-   Go to <https://github.com/settings/tokens> and click "Generate token".

-   Or using the `usethis` package:

```{r eval=FALSE}

## install if needed:
## install.packages("usethis")

usethis::create_github_token()

```

<br>

#### Paste your PAT into the Git credential store

```{r eval=FALSE}
gitcreds::gitcreds_set()

```

### Third Step

#### Tell git who you are:

Command line

```{r eval=FALSE}

git config --global user.name 'diegoxx'
git config --global user.email 'diego@example.xx'
git config --global --list

```

Or:

```{r eval=FALSE}


usethis::use_git_config(user.name = "diegoxx", user.email = "diego@example.xx")


```
:::

# [You are now ready to go]{style="color:#F4BA02;"} {background-image="./images/git-factory.png" background-opacity="0.3"} 

::: footer
::: {style="text-align:right;"}
[Illustration: Alisson Horst](https://allisonhorst.com/git-github)
:::
:::